---
title: "Exploratory Data Analysis"
author: "Woomy Michel :)"
date: "2023-11-27"
output: html_document
---

```{r}
library(dplyr)
library(ggplot2)
library(readr)
library(readxl)
```
Reading in the two datasets.
```{r}
media_item = read.delim("cleaned_dataset.txt", sep = "", header = TRUE)
county_data = read_xlsx("counties.xlsx")
state_abbreviations = read.csv("state_abbreviations.csv")
```
Merging on the county and state name, but first we have to change the state abbreviations so they'll match.
```{r}
media_item$State[media_item$State == "D.C."] <- "DC"
```

```{r}
media_abb = left_join(media_item, state_abbreviations, by = c("State" = "Abb_State"))
```
**Exploratory Data Analysis**

In this section, we will explore trends in the dataset. Some questions that we will explore are:
- Between 1865 and 1965, what was the total number of Black owned newspapers?
- Which counties had the greatest number of Black owned newspapers?
- Which states had the greatest number of Black owned newspapers?
- Which newspaper was published most?
- In which years, were Black newspapers mass produced?
- Are there any trends across the years? Across certain regions?

First, let's see how many Black newspapers there were altogether. 

Between 1865 and 1965, there were 276 Black newspapers.
```{r}
media_abb %>% select(Newspaper, County, Full_State) %>% distinct()
```
Now let's see the number of newspapers by county.

It appears that between 1865 and 1965, the District of Columbia, Marrion County (IN), Ramsey County (MN) and Cook County (IL) published the most Black owned newspapers. 

```{r}
media_abb %>% select(Full_State, County) %>% group_by(Full_State, County) %>% count() %>% arrange(desc(n))
```
Let's look at the number of Black owned newspapers by state. 

North Carolina, Illinois and Virginia have produced the greatest number of Black newspapers between 1865 and 1965, while Delaware, Oregon and Arkansas produced the smallest number of Black newspapers. 
```{r}
state_level  = media_abb %>% select(State) %>% group_by(State) %>% count() %>% arrange(desc(n))

ggplot(state_level, aes(reorder(State, n), n)) + geom_col() + coord_flip() + xlab("States") + ylab("Number of Black Owned Newspapers") + ggtitle("Number of Black Owned Newspapers by State") + theme(plot.title = element_text(hjust = 0.5)) 
```
Let's look at the distribution throughout the years.

To put into perspective, the first Black owned and operated newspaper in the United States was founded in 1827. It was established the same year that slavery was abolished in New York State. 


```{r}
newspapers = media_abb %>% select(Year) %>% group_by(Year) %>% count()
```
Line Graph.
```{r}
ggplot() + geom_line(aes(y=n, x=Year), data = newspapers) + geom_point() + xlab("Year") + ylab("Number of Newspapers") + ggtitle("Number of Black Newspapers per Year") + xlim(1865, 1965) + theme(plot.title = element_text(hjust = 0.5))
```
Let's look at the average number of newspapers produced.
```{r}
avg_newspapers = media_abb %>% select(County, State) %>% group_by(County, State) %>% count() 

mean(avg_newspapers$n)
median(avg_newspapers$n)
```
Let's see which Black newspaper company published the most newspapers.

The newspapers that were most published were "The Indianapolis Recorder" (Marion County), "New York Age" (New York County) and the "Washington Afro American" (District of Columbia). Each of these Black newspapers, produced 50 or more newspapers between 1865 and 1965.
```{r}
media_abb %>% select(Newspaper, County, Full_State) %>% group_by(Newspaper,County, Full_State) %>% count() %>% arrange(desc(n))
```

Now that we've done our EDA, we will determine which counties had limited resources publishing Black newspapers. For the sake of our analysis, we will round the average number of newspapers published to the nearest integer. Counties that produced no newspapers will receive a 1 and counties that produced more a Black newspaper will receive a 0.

```{r}
county = media_abb %>% select(County, Full_State) %>% group_by(County, Full_State) %>% count() %>% mutate(Racism = 0)

df = county %>% select(Full_State, County, Racism)

#changing the spelling so it matches the county dataset
df$Full_State[df$Full_State == "District of Columbia"] <- "District Of Columbia"
```
Now let's look back at the county dataset. Here we are joining the two datasets.
```{r}
df2 = left_join(county_data, df, by = c("STATE" = "Full_State", "ALLCOUNTIES" = "County"))

#temp_df2 = df2 %>% select(STATE, ALLCOUNTIES, Racism)
#colnames(temp_df2) = c("Full_State", "County", "Racism")
#setdiff(df, temp_df2)
```
Since NA values were returned for the Racism column for certain counties, we can assume that no Black newspapers were published for those counties, thus we will assign a 1 to them.
```{r}
df2$Racism[is.na(df2$Racism)] <- 1
df2$Racism = as.factor(df2$Racism)
```
Saving the CSV file.
```{r}
write.csv(df2, "MM_LRA1.csv")
```
More Exploratory Data Analysis.

Let's look at the distribution of 0s and 1s in the dataset. As highlighted by the bar graph, an overwhelming number of counties (3131) have not published a Black newspaper. Only 131 counties in the dataset have published at least 1 or more Black newspapers.
```{r}
df2 %>% select(Racism) %>% group_by(Racism) %>% count() %>% ggplot(aes(x=Racism, y=n), fill = Racism) + geom_bar(stat = "identity") + xlab("") + ylab("Number of Counties") + scale_x_discrete(labels = c("At least 1 Black newspaper", "No Black newspapers")) + ggtitle("Black Newspapers Vs No Black Newspapers (1865-1965)") + theme(plot.title = element_text(hjust = 0.5)) 

df2 %>% select(Racism) %>% group_by(Racism) %>% count()
```
Now let's make some maps of the data. Here, we will explore how Black owned newspapers change over the years. Some questions to keep in mind:

- Is there an introduction of more Black newspapers across various counties and regions throughout the years?

```{r}
left_join(media_abb, county_data, by=c("Full_State" = "STATE", "County"="ALLCOUNTIES"))
```







