---
title: "Media Item"
author: "Woomy Michel :)"
date: "2023-11-14"
output: html_document
---
Installing packages.
```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(scrutiny)
library(skimr)
```
Loading data and cleaning it.
```{r}
media = read.delim("Media Item.txt", sep= ":" , header = FALSE)

new_media = separate(media, col = V1, into=c("Newspaper Name", "City", "State"), sep=",")

new_media_2 = separate_rows(new_media, V2, convert = TRUE)
```
Removing the parentheses from the newspaper name and removing the whitespace from the city and state columns.
```{r}
string = new_media_2$`Newspaper Name`
new_string = gsub("\\s*\\([^\\)]+\\)", "", string)
new_string = as.data.frame(new_string)


city = new_media_2$City
city = str_squish(city)
city = as.data.frame(city)

state = new_media_2$State
state = str_squish(state)
state = as.data.frame(state)
```
Combining the two datasets. 
```{r}
df = cbind(new_string, city, state, new_media_2)
```
Changing the column names.
```{r}
df = df %>% select(new_string, city, state, V2)
names(df) = c("Newspaper", "City", "State", "Year")
```
Working with the MM.LRA1 item, so we only need years between 1865 and 1965.
```{r}
clean_df = df %>% select(everything()) %>% filter(Year>=1865 & Year<=1965) %>% distinct()
```
Assigning the counties for each of the cities in the dataset.
```{r}
clean_df$County = ""
```

```{r}
clean_df$County[clean_df$City == "New Orleans"] <- "Orleans"

clean_df$County[clean_df$City == "Philadelphia"] <- "Philadelphia"

clean_df$County[clean_df$City == "Nashville"] <- "Davidson"

clean_df$County[clean_df$City == "San Francisco"] <- "San Francisco"

clean_df$County[clean_df$City == "Hampton"] <- "Elizabeth City" 

clean_df$County[clean_df$City == "Little Rock"] <- "Pulaski"

clean_df$County[clean_df$City == "Saint Paul"] <- "Ramsey" 

clean_df$County[clean_df$City == "Charleston" & clean_df$State == "SC"] <- "Charleston"

clean_df$County[clean_df$City == "Charleston" & clean_df$State == "WV"] <- "Kanawha"

clean_df$County[clean_df$City == "Cincinnati"] <- "Hamilton"

clean_df$County[clean_df$City == "Savannah"] <- "Chatham" 

clean_df$County[clean_df$City == "Vidalia"] <- "Concordia"

clean_df$County[clean_df$City == "St. Martinsville"] <- "St Martin"

clean_df$County[clean_df$City == "Fayetteville"] <- "Cumberland"

clean_df$County[clean_df$City == "Orangeburg"] <- "Orangeburg"

clean_df$County[clean_df$City == "Austin"] <- "Travis" 

clean_df$County[clean_df$City == "Georgetown"] <- "Georgetown"

clean_df$County[clean_df$City == "Maryville"] <- "Blount" 

clean_df$County[clean_df$City == "Washington"] <- "District Of Columbia"

clean_df$County[clean_df$City == "Raleigh"] <- "Wake"

clean_df$County[clean_df$City == "Wilmington"] <- "New Hanover" 

clean_df$County[clean_df$City == "Petersburg"] <- "Dinwiddie, Prince George" 

clean_df$County[clean_df$City == "Norfolk"] <- "Norfolk City"

clean_df$County[clean_df$City == "Baltimore"] <- "Baltimore City"

clean_df$County[clean_df$City == "Topeka" | clean_df$City == "North Topeka"] <- "Shawnee"

clean_df$County[clean_df$City == "Salt Lake City"] <- "Salt Lake"

clean_df$County[clean_df$City == "Chicago"] <- "Cook"

clean_df$County[clean_df$City == "Helena"] <- "Lewis And Clark"

clean_df$County[clean_df$City == "Logansport"] <- "Cass"

clean_df$County[clean_df$City == "Louisville"] <- "Jefferson" 

clean_df$County[clean_df$City == "Springfield" & (clean_df$State == "MO")] <- "Greene" 

clean_df$County[clean_df$City == "Seattle"] <- "King"

clean_df$County[clean_df$City == "Columbus" & (clean_df$State == "OH")] <- "Franklin" 

clean_df$County[clean_df$City == "Indianapolis"] <- "Marion"

clean_df$County[clean_df$City == "Vicksburg"] <- "Warren"

clean_df$County[clean_df$City == "Huntsville"] <- "Madison" 

clean_df$County[clean_df$City == "Des Moines"] <- "Polk" 

clean_df$County[clean_df$City == "Chattanooga"] <- "Hamilton"

clean_df$County[clean_df$City == "Langston City"] <- "Logan" 

clean_df$County[clean_df$City == "Laurinburg"] <- "Scotland"

clean_df$County[clean_df$City == "Boydton"] <- "Mecklenburg"

clean_df$County[clean_df$City == "Wichita"] <- "Sedgwick" 

clean_df$County[clean_df$City == "Weldon"] <- "Halifax"

clean_df$County[clean_df$City == "Knoxville"] <- "Knox" 

clean_df$County[clean_df$City == "New York"] <- "New York"

clean_df$County[clean_df$City == "Nicodemus"] <- "Graham"

clean_df$County[clean_df$City == "New Bern"] <- "Craven"

clean_df$County[clean_df$City == "Columbia" & clean_df$State == "SC"] <- "Richland"

clean_df$County[clean_df$City == "Omaha"] <- "Douglas"

clean_df$County[clean_df$City == "Richmond"] <- "Henrico, Chesterfield"

clean_df$County[clean_df$City == "Asheville" | clean_df$City == "Ashville"] <- "Buncombe" 

clean_df$County[clean_df$City == "Springfield" & clean_df$State == "IL"] <- "Sangamon" 

clean_df$County[clean_df$City == "Atlanta"] <- "Fulton"

clean_df$County[clean_df$City == "New Albany" & clean_df$State == "IN"] <- "Floyd"

clean_df$County[clean_df$City == "Lacrosse"] <- "La Crosse"

clean_df$County[clean_df$City == "Boston"] <- "Suffolk"

clean_df$County[clean_df$City == "Willmington"] <- "New Castle"

clean_df$County[clean_df$City == "St. Louis"] <- "St Louis" 

clean_df$County[clean_df$City == "Augusta"] <- "Richmond"

```

Noticing that the file won't format "The Colorado Stateman" properly and there are numerous duplicates. So removing this from the dataset.
```{r}
clean_df = clean_df %>% select(everything()) %>% filter(Newspaper != "The Colorado Stateman Denver")
clean_df = clean_df %>% select(everything()) %>% filter(State != "UT and Chicago")
```

```{r}
clean_df$County[clean_df$City == "Columbus" & clean_df$State == "GA"] <- "Muscogee"

clean_df$County[clean_df$City == "Denver"] <- "Denver"

clean_df$County[clean_df$City == "Jackson" & clean_df$State == "TN"] <- "Madison"

clean_df$County[clean_df$City == "Jacksonville"] <- "Duval"

clean_df$County[clean_df$City == "Pensacola"] <- "Escambia"

clean_df$County[clean_df$City == "Brandon" & clean_df$State == "MS"] <- "Rankin"

clean_df$County[clean_df$City == "Cleveland"] <- "Cuyahoga"

clean_df$County[clean_df$City == "Tampa"] <- "Hillsborough"

clean_df$County[clean_df$City == "Brunswick"] <- "Glynn"

clean_df$County[clean_df$City == "Waycross"] <- "Ware"

clean_df$County[clean_df$City == "Houston"] <- "Harris"

clean_df$County[clean_df$City == "Dallas"] <- "Dallas"

clean_df$County[clean_df$City == "Jackson" & clean_df$State == "TN"] <- "Madison"

clean_df$County[clean_df$City == "Kansas City"] <- "Jackson"

clean_df$County[clean_df$City == "Owensboro"] <- "Daviess"

clean_df$County[clean_df$City == "Lexington"] <- "Fayette"

clean_df$County[clean_df$City == "Macon" & clean_df$State == "GA"] <- "Bibb"

clean_df$County[clean_df$City == "Metropolis"] <- "Massac"

clean_df$County[clean_df$City == "Macon" & clean_df$State == "MS"] <- "Noxubee"

clean_df$County[clean_df$City == "Montgomery"] <- "Montgomery"

clean_df$County[clean_df$City == "Muskogee Indian Territory"] <- "Muskogee"

clean_df$County[clean_df$City == "Butte"] <- "Silver Bow"

clean_df$County[clean_df$City == "Baton Rouge"] <- "East Baton Rouge"

clean_df$County[clean_df$City == "Xenia"] <- "Greene"

clean_df$County[clean_df$City == "Corsicana"] <- "Navarro"

clean_df$County[clean_df$City == "Guthrie"] <- "Logan"

clean_df$County[clean_df$City == "Parsons"] <- "Labette"

clean_df$County[clean_df$City == "Waco"] <- "McLennan"

clean_df$County[clean_df$City == "Pink Bluff"] <- "Jefferson"

clean_df$County[clean_df$City == "Martinsburg"] <- "Berkeley"

clean_df$County[clean_df$City == "Portland"] <- "Multnomah"

clean_df$County[clean_df$City == "Columbia" & clean_df$State == "MO"] <- "Boone"

clean_df$County[clean_df$City == "Rock Hill"] <- "York"

clean_df$County[clean_df$City == "Sedalia"] <- "Pettis"

clean_df$County[clean_df$City == "Columbus" & clean_df$State == "SC"] <- "Richland"

clean_df$County[clean_df$City == "Galveston"] <- "Galveston"

clean_df$County[clean_df$City == "Littleton"] <- "Halifax"

clean_df$County[clean_df$City == "Tulsa"] <- "Tulsa"

clean_df$County[clean_df$City == "Minneapolis"] <- "Hennepin"

clean_df$County[clean_df$City == "Laurel"] <- "Jones"

clean_df$County[clean_df$City == "Cary"] <- "Sharkey"

clean_df$County[clean_df$City == "Colorado Springs"] <- "El Paso"

clean_df$County[clean_df$City == "Birmingham"] <- "Shelby"

clean_df$County[clean_df$City == "Yazoo City"] <- "Yazoo"

clean_df$County[clean_df$City == "Phoenix"] <- "Maricopa"

clean_df$County[clean_df$City == "Athens"] <- "Clarke"

clean_df$County[clean_df$City == "Greensboro"] <- "Guilford"

clean_df$County[clean_df$City == "Oklahoma City"] <- "Oklahoma"

clean_df$County[clean_df$City == "Los Angeles"] <- "Los Angeles"

clean_df$County[clean_df$City == "Durham"] <- "Durham"

clean_df$County[clean_df$City == "Dayton"] <- "Montgomery"

clean_df$County[clean_df$City == "Greenville" & clean_df$State == "MS"] <- "Washington"

clean_df$County[clean_df$City == "Detroit"] <- "Wayne"

clean_df$County[clean_df$City == "Meridian"] <- "Lauderdale"

clean_df$County[clean_df$City == "Elizabeth City"] <- "Pasquotank"

clean_df$County[clean_df$City == "Evansville"] <- "Vanderburgh"

clean_df$County[clean_df$City == "Gainesville"] <- "Alachua"

clean_df$County[clean_df$City == "Miami"] <- "Dade, Miami-Dade County"
```

```{r}
clean_df$County[clean_df$City == "Springfield" & clean_df$State == "MA"] <- "Hampden"

clean_df$County[clean_df$City == "Galesburg" ] <- "Knox"

clean_df$County[clean_df$City == "Jackson" & clean_df$State == "MS"] <- "Hinds"

clean_df$County[clean_df$City == "Keystone" ] <- "McDowell"

clean_df$County[clean_df$City == "St. Paul" ] <- "Ramsey"

clean_df$County[clean_df$City == "Charlottesville" ] <- "Albemarle"

clean_df$County[clean_df$City == "San Antonio" ] <- "Bexar"

clean_df$County[clean_df$City == "Mound Bayou" ] <- "Bolivar"

clean_df$County[clean_df$City == "Lincoln" ] <- "Lancaster"

clean_df$County[clean_df$City == "Madison" ] <- "Dane"

clean_df$County[clean_df$City == "Buffalo" ] <- "Erie"

clean_df$County[clean_df$City == "Forest City" ] <- "Rutherford"

clean_df$County[clean_df$City == "New Albany" ] <- "Union"

clean_df$County[clean_df$City == "Hartford" ] <- "Hartford"

clean_df$County[clean_df$City == "Champaign" ] <- "Champaign"

clean_df$County[clean_df$City == "Winston-Salem" ] <- "Forsyth"

clean_df$County[clean_df$City == "Robbins" ] <- "Cook"

clean_df$County[clean_df$City == "Roanoke" ] <- "Roanoke"
```
Since we stored multiple counties in one row, we'll separate them so each county will have its own row.
```{r}
clean_df = clean_df %>% separate_rows(County, sep = ",")

#removing whitespace
clean_county = str_squish(clean_df$County)

clean_df = cbind(clean_df, clean_county)
clean_df = clean_df %>% select(Newspaper, City, State, Year, clean_county)

colnames(clean_df)[5] <- "County"
```

```{r}
write.table(clean_df, file = "cleaned_dataset.txt", sep = "", row.names = FALSE, col.names = TRUE)
```


